### 2016-06-07 filters.tex
notions for multi-server setting

\heading{Security in multiple-server settings. }
\begin{figure}
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPSecHash{B,\ell}{\distr{U}{n}, A}$}\\
$S_1,S_2,\ldots,S_\ell \getsr \distr{U}{n}$\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$\mathcal{C} \gets \emptyset$\\
for $i=1$ to $\ell$\\
\nudge $M_i \gets \Rep^{\HashOracle}(S_i)$\\
$(i,x) \getsr A^{\QryOracle,\CorruptOracle}()$\\
if $i \not\in \mathcal{C} \wedge \Qry^{\HashOracle}(M_i,x)=1$ then \\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(i,x)$}\\
Ret $\Qry^{\HashOracle}(M_i,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\

\medskip
\oracle{$\CorruptOracle(i,x)$}\\
$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
Ret $S_i,M_i$\\
}
}
%%%%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPPubHashBB{B,\ell}{\distr{U}{n}, A}$}\\
$S_1,S_2,\ldots,S_\ell \getsr \distr{U}{n}$\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$\mathcal{C} \gets \emptyset$\\
for $i=1$ to $\ell$\\
\nudge $M_i \gets \Rep^{\HashOracle}(S_i)$\\
$(i,x) \getsr A^{\QryOracle,\HashOracle,\CorruptOracle}()$\\
if $i \not\in \mathcal{C} \wedge \Qry^{\HashOracle}(M_i,x)=1$ then \\
\nudge Ret 1\\ 
Ret 0
}
%
{
\oracle{$\QryOracle(i,x)$}\\
Ret $\Qry^{\HashOracle}(M_i,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\

\medskip
\oracle{$\CorruptOracle(i,x)$}\\
$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
Ret $S_i,M_i$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPPubHash{B,\ell}{\distr{U}{n}, A}$}\\
$S_1,S_2,\ldots,S_\ell \getsr \distr{U}{n}$\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$\mathcal{C} \gets \emptyset$\\
for $i=1$ to $\ell$\\
\nudge $M_i \gets \Rep^{\HashOracle}(S_i)$\\
$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(\{h_1,h_2,\ldots,h_k\})$\\
if $i \not\in \mathcal{C} \wedge \Qry^{\HashOracle}(M_i,x)=1$ then \\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(i,x)$}\\
Ret $\Qry^{\HashOracle}(M_i,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\

\medskip
\oracle{$\CorruptOracle(i,x)$}\\
$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
Ret $S_i,M_i$\\
}
}
\caption{False-positive security for an $(n,k,m)$-filter~$B$ in the multiple-server setting.  (Three variations, depending on access to/knowledge of hash functions.) In these notions, the same hash functions are used across multiple servers, and each server has its own, independent set to represent. \textcolor{cyan}{This is a reasonable(?) modeling of the Squid setting.}}
\label{fig:fp-filter}
\end{figure}

>>>>

\heading{Security in multiple-server settings. }
\begin{figure}
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPSecHash{B_1,B_2,\ldots,B_\ell}{\distr{U}{n}, A}$}\\
$\mathcal{C} \gets \emptyset$\\
for $i=1$ to $\ell$\\
\nudge $S_i \getsr \distr{U}{n}$\\
\nudge $ \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
\nudge $M_i \gets \Rep_i^{\HashOracle}(S_i)$\\
$(i,x) \getsr A^{\QryOracle,\CorruptOracle}()$\\
if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle}(M_i,x)=1$ then \\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(i,x)$}\\
Ret $\Qry_i^{\HashOracle}(M_i,x)$\\

\medskip
\oracle{$\HashOracle(i,j,x)$}\\
Ret $h^i_j(x)$\\

\medskip
\oracle{$\CorruptOracle(i,x)$}\\
$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
Ret $S_i,M_i,\{h^i_1,\ldots,h^i_k\}$\\
}
}
%%%%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPPubHashBB{B_1,B_2,\ldots, B_\ell}{\distr{U}{n}, A}$}\\
$\mathcal{C} \gets \emptyset$\\
for $i=1$ to $\ell$\\
\nudge $S_i \getsr \distr{U}{n}$\\
\nudge $ \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
\nudge $M_i \gets \Rep_i^{\HashOracle}(S_i)$\\
$(i,x) \getsr A^{\QryOracle,\HashOracle,\CorruptOracle}()$\\
if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle}(M_i,x)=1$ then \\
\nudge Ret 1\\ 
Ret 0
}
%
{
\oracle{$\QryOracle(i,x)$}\\
Ret $\Qry^{\HashOracle}(M_i,x)$\\

\medskip
\oracle{$\HashOracle(i,j,x)$}\\
Ret $h^i_j(x)$\\

\medskip
\oracle{$\CorruptOracle(i,x)$}\\
$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
Ret $S_i,M_i$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPPubHash{B_1,B_2,\ldots,B_\ell}{\distr{U}{n}, A}$}\\
$\mathcal{C} \gets \emptyset$\\
for $i=1$ to $\ell$\\
\nudge $S_i \getsr \distr{U}{n}$\\
\nudge $ \mathcal{H}_i \gets \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
\nudge $M_i \gets \Rep_i^{\HashOracle}(S_i)$\\
$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(\mathcal{H}_1,\mathcal{H}_2,\ldots,\mathcal{H}_\ell)$\\
if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle}(M_i,x)=1$ then \\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(i,x)$}\\
Ret $\Qry^{\HashOracle}(M_i,x)$\\

\medskip
\oracle{$\HashOracle(i,j,x)$}\\
Ret $h^i_j(x)$\\

\medskip
\oracle{$\CorruptOracle(i,x)$}\\
$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
Ret $S_i,M_i$\\
}
}
\caption{False-positive security for an $(n,k,m)$-filter~$B$ in the multiple-server setting.  (Three variations, depending on access to/knowledge of hash functions.) }
\label{fig:fp-filter}
\end{figure}
